Exploring Pocket Size and Jean Prices for Men and Women

### 2024-04-24 paper/paper.qmd
final paper

---
title: "Jean Pockets and Gender"
subtitle: "subtitle"
author: Hari Lee Robledo
thanks: "Code and data are available at: https://github.com/hari-lr/pockets-and-gender"
date: today
date-format: long
abstract: "This paper explores the intersection of gender, fashion, and pricing dynamics, focusing on pocket inequality in jeans. The study investigates whether there is a correlation between pocket size and jean prices for men and women. Utilizing data collected by Diehm & Thomas (2018) from 20 popular US jeans brands, the analysis employs linear regression models, standard deviation and averages to examine the relationship between pocket area and price. The findings reveal that pocket area is not a significant predictor of price for either men's or women's jeans, indicating complex pricing dynamics beyond pocket considerations. The implications of these findings underscore the need for further discussions surrounding the pink tax and pocket inequality by providing empirical evidence of pricing disparities. While the average price of women's jeans appears slightly lower than men's, the considerable variability in prices within each gender category suggests deeper complexities."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

>>>>

---
title: "Exploring Pocket Size and Jean Prices for Men and Women"
subtitle: "An Analysis of the 2018 *Women´s Pockets are Inferior* Data"
author: Hari Lee Robledo
thanks: "Code and data are available at: https://github.com/hari-lr/pockets-and-gender"
date: today
date-format: long
abstract: "This paper explores the intersection of gender, fashion, and pricing dynamics, focusing on pocket inequality in jeans. The study investigates whether there is a correlation between pocket size and jean prices for men and women. Utilizing data collected by Diehm & Thomas (2018) from 20 popular US jeans brands, the analysis employs linear regression models, standard deviation and averages to examine the relationship between pocket area and price. The findings reveal that pocket area is not a significant predictor of price for either men's or women's jeans, indicating complex pricing dynamics beyond pocket considerations. The implications of these findings underscore the need for further discussions surrounding the pink tax and pocket inequality by providing empirical evidence of pricing disparities. While the average price of women's jeans appears slightly lower than men's, the considerable variability in prices within each gender category suggests deeper complexities."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
